---
title: "Reg-One-Markdown"
author: "Jamy Anzaldo"
date: "April 25, 2019"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
```

## First Read in the data

```{r}
theData <- read.csv(file="mydata.csv",header = TRUE)
```

Now we are gonna look at what relations exist between our variables with plots

## Including Plots

You can also embed plots, for example:

##ggplot SIMS~ARM
```{r}
basicNN <- ggplot(theData,aes(x=SIMS,y=ARM))
```
##SIMS and ARM plot

```{r}
basicNN + geom_point() 
basicNN + geom_point() + geom_lm()
basicNN + geom_point() + geom_lm()+ geom_smooth()
```

##Lets take a look at how SIMS and GRIP correlate

```{r}
basicN2 <- ggplot(theData,aes(x=SIMS,y=GRIP))
```

##SIMS and GRIP plots

```{r}
basicN2 + geom_point() 
basicN2 + geom_point() + geom_lm()
basicN2 + geom_point() + geom_lm()+ geom_smooth()
``` 

##Lets take a look at how SIMS and GRIP + ARM correlate

```{r}
basicN3 <- ggplot(theData,aes(x=SIMS,y=GRIP + ARM))
```
##Sims and GRIP + ARM plots
```{r}
basicN3 + geom_point() 
basicN3 + geom_point() + geom_lm()
basicN3 + geom_point() + geom_lm()+ geom_smooth()
``` 

# Build 3 regression Models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP

```{r}
M1 <- lm(SIMS ~ ARM, data=theData) 
summary.lm(M1)
summary(M1)$adj.r.squared
```
```{r}
M2 <- lm(SIMS ~ GRIP, data=theData) 
summary.lm(M2)
summary(M2)$adj.r.squared
```  
```{r}
M3 <- lm(SIMS ~ ARM + GRIP, data=theData) 
summary.lm(M2)
summary(M2)$adj.r.squared
``` 

## now we'll give a value of 104  for GRIP and 98 for ARM to begin finding the 95% interval for sims

```{r}
new <- data.frame(ARM=c(98),GRIP=c(104))
```
#### Now lets see what the three models predict - Here is M1

```{r}
predict.lm(M1,new)
```
#AND here is m2
```{r}
predict.lm(M2,new)
``` 
#Now we find the 95% interval for m1 & m2
#m1
```{r}
predict.lm(M1,new,interval = "prediction",se.fit = TRUE)
```
95% interval for M1 is (-1.185858, 3.689886)
#M2
```{r}
predict.lm(M2,new,interval = "prediction",se.fit = TRUE)
```
95% interval for M2 is (-2.64982, 2.486771)
 
Which means Arm is a better predictor of SIMS than GRIP is.

###Now we will compare Model1 with Model3 using anova
```{r}
anova(M1,M3)
```
since adding the GRIP o Arm it redued the room for error and since the p value is 4.994e-06 (which is less than .05) it means that there is a significant diffrencebetween model 1 and model 3